Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
adding comments.
revert mis operation: Conclusion is back.
using quantified.

@@

@@

\noindent To specify properties, we also propose a new markup. In this paper, we
use the {\tt prop>} prefix. We can write properties which do not take
parameters as follows:

@@

\noindent Of course, we allowed properties which take parameters by
using closed lambda terms.
Type signatures can be specified for each parameter:

@@

@@

%% It is enough to test properties which do not have parameters just one.
%% However, QuickCheck 2.3 or earlier tests
%% properties which do not have parameters 100 times.
%% More precisely, the evaluation results are memorized and they are
%% compared with {\tt True} 100 times.
%% The current maintainer of QuickCheck modified so that
%% properties which do not have parameters
%% are tested just once in its source repository.
%% This feature will be available in the future release.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \section{Conclusion}

%% \appendix

%% \section{Package Survey}

%% TBD

@@

We are grateful to David Waern, Haddock's maintainer, for reviewing our patches
and accepting our patches to Haddock.
We would like to thank
Nick Smallbone for having improved QuickCheck so that
properties which do not have parameters are tested just once.

>>>>

\item[non-quantified property]
    Property which does not take parameters.

\item[quantified property]
    Property which takes parameters.

@@

\begin{quote}
\emph{kazu: if this subsection is long, we can remove the following paragraph.}
\end{quote}

@@

\noindent To specify properties, we also propose a new markup. In this paper, we
use the {\tt prop>} prefix. We can write non-quantified properties as follows:

@@

\noindent Of course, we allowed quantified properties by using closed
lambda terms.
Type signatures can be specified for each parameter:

@@

\begin{quote}
\emph{kazu: are parentheses necessary? how about following?}
\begin{verbatim}
  launchMissiles >>=
  (`shouldBe` Left "not implemented")
  launchMissiles `shouldReturn` Left "not implemented"
\end{verbatim}
\end{quote}

@@

%% It is enough to test non-quantified properties just one.
%% However, QuickCheck 2.3 or earlier tests
%% non-quantified properties 100 times.
%% More precisely, the evaluation results are memorized and they are
%% compared with {\tt True} 100 times.
%% The current maintainer of QuickCheck modified so that
%% non-quantified properties
%% are tested just once in its source repository.
%% This feature will be available in the future release.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}

TBD

@@

We are grateful to David Waern, Haddock's maintainer, for reviewing our patches
and accepting our patches to Haddock.
We would like to thank
Nick Smallbone for having improved QuickCheck so that
non-quantified properties are tested just once.
